The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2010-06-04 script/de/script-de.tex
Script[de+en]: Finished to insert the chapter with the plots about the quantity of primes in higher ranges, and the according references.
fixed spacing in \author{}

% Formatierung der Fußnoten
\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage[hyphens]{url} % options "hyphens" enables linebreaks in \url{}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
\usepackage{float}
\usepackage{shorttoc}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,plainpages=false,hyperfootnotes=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels, plainpages=false and, hyperfootnotes=false and place hyperref after float.
%Option debug helps finding problems.

@@

\author{ %
	{\LARGE (c) Prof.\ Bernhard Esslinger (Mitautor und Herausgeber)} \\
	\vspace{5pt}
	{\LARGE und das CrypTool Entwickler-Team, 1998-2010} \\
	\vspace{5pt}
	{\LARGE Frankfurt am Main} \\*[1ex]
	\vspace{5pt}
	\url{www.cryptool.org}
}

>>>>

% Formatierung der Fußnoten
\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage[hyphens]{url} % options "hyphens" enables linebreaks in \url{}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
\usepackage{float}
\usepackage{subfig}
\usepackage{shorttoc}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,plainpages=false,hyperfootnotes=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels, plainpages=false and, hyperfootnotes=false and place hyperref after float.
%Option debug helps finding problems.

@@

\author{ %
	{\LARGE (c) Prof.\ Bernhard Esslinger (Mitautor und Herausgeber)}\\[5pt]
	{\LARGE und das CrypTool Entwickler-Team, 1998-2010}\\[5pt]
	{\LARGE Frankfurt am Main}\\*[15pt]
	\url{www.cryptool.org}
}

### 2010-06-04 script/en/script-en.tex
fixed spacing in \author{}

% Hier wird \vspace{32pt} einfach ignoriert
\author{ % Die Klammer zur Fontänderung funktioniert bei author nur einzeilig im Gegensatz zu title?!
        {\LARGE Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor)}\\
	\vspace{5pt}  % Dies wirkt sich nicht aus ???????????
        {\LARGE and the CrypTool Development Team, 1998-2010}\\
	\vspace{5pt}
        {\LARGE Frankfurt am Main, Germany} \\*[1ex]
	\vspace{5pt}
        \url{www.cryptool.org}
}

>>>>

% Hier wird \vspace{32pt} einfach ignoriert
\author{ % Die Klammer zur Fontänderung funktioniert bei author nur einzeilig im Gegensatz zu title?!
        {\LARGE Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor)}\\[5pt]
        {\LARGE and the CrypTool Development Team, 1998-2010}\\[5pt]
        {\LARGE Frankfurt am Main, Germany} \\*[15pt]
        \url{www.cryptool.org}
}
